On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 paper.tex
Ack
Acknowledgements for Yo-Sub added.
Intro is in a good shape
Intro is done. I may add something more, but not needed.

\begin{figure}[tb]
\begin{tikzpicture}

\draw[-latex] (origin) -- ++(0:5) node[below] {$\delta$}; 
\node at (2, -0.2) {1};
\node at (4, -0.2) {2 and 3};
\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
\node at (-0.2, 1) {1};
\node at (-0.2, 2) {2};
\node at (-0.2, 3) {3};
\node at (-0.2, 4) {4};

%Results
\node at (2, 4) {$3n(n+1)+1$};
\node at (2, 3) {$4n+14$};
\node at (2, 2) {$9n(3n+1)+1$};
\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};

\node at (4, 1) {$O(n^2)$};

\end{tikzpicture}
\caption{Summary of the results.}
\label{fig:summary}
\end{figure}

@@

Results on this problem are summarized in Fig.~\ref{fig:summary}.

@@

\begin{corollary}
	For fixed $\delta$ and $\alpha$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
\end{corollary}
\begin{proof}
	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
\end{proof}

@@

\section{Case of arity $1$}

@@

\section{Case of delay $1$}
\input{tt_intro}
\input{tt_theorem}

>>>>

@@

\begin{figure}[tb]
  \begin{center}
    \begin{tikzpicture}
      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

      \draw[dashed] (0,0)--(1.5,0);
      \draw[dashed] (1.5,0)--(3,0);
      \draw[dashed] (3,0)--(4.5,0);
      \draw[dashed] (4.5,0)--(6,0);
      \draw[->] (0,0)--(60:0.75);
      \draw[->] (1.5,0)--++(60:0.75);
      \draw[->] (3,0)--++(60:0.75);
      \draw[->] (4.5,0)--++(60:0.75);
      \draw (0,0)--(60:1.5);
      \draw (1.5,0)--++(60:1.5);
      \draw (3,0)--++(60:1.5);
      \draw (4.5,0)--++(60:1.5);

      \begin{scope}[shift=(60:1.5)]
        \fill (0,0) circle[radius = 0.1];
        \fill (1.5,0) circle[radius = 0.1];
        \fill (3,0) circle[radius = 0.1];
        \fill (4.5,0) circle[radius = 0.1];
        \draw[dashed] (0,0)--(1.5,0);
        \draw[dashed] (1.5,0)--(3,0);
        \draw[dashed] (3,0)--(4.5,0);
        \draw[->] (0,0)--(-60:0.75);
        \draw[->] (1.5,0)--++(-60:0.75);
        \draw[->] (3,0)--++(-60:0.75);
        \draw[->] (4.5,0)--++(-60:0.75);

        \draw (0,0)--(-60:1.5);
        \draw (1.5,0)--++(-60:1.5);
        \draw (3,0)--++(-60:1.5);
        \draw (4.5,0)--++(-60:1.5);
      \end{scope}

    \end{tikzpicture}
    \caption{The zig-zag conformation. This is the only one infinite conformation foldable deterministically by an unary oritatami ssytem at delay 1 and arity 2.}
    \label{TTT_zigzag}
  \end{center}
\end{figure}

\begin{figure}[tb]
\centering
\begin{tikzpicture}

\draw[-latex] (origin) -- ++(0:10) node[below] {$\delta$}; 
\node at (2, -0.2) {1};
\node at (4, -0.2) {2 and 3};
\node at (6, -0.2) {4 and larger}; 
\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
\node at (-0.2, 1) {1};
\node at (-0.2, 2) {2};
\node at (-0.2, 3) {3};
\node at (-0.2, 4) {4};

%Results
\node at (2, 4) {$3n(n{+}1){+}1$};
\node at (2, 3) {$4n{+}14$};
\node at (2, 2.2) {$\infty$ but zigzag after};
\node at (2, 1.8) {$(27n^2{+}9n{+}1)$-th bead};
\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};

\node at (4, 1) {$3n^2{+}4n{+}1$};

\end{tikzpicture}
\caption{Upper bounds on the length of a conformation foldable by a deterministic unary oritatami system at delay $\delta$ and arity $\alpha$.
At any combination of delay and arity without anything written, no upper bound is known yet.
}
\label{fig:summary}
\end{figure}
In this paper, we will solve this problem partially at arity 1 in Sect.~\ref{sect:arity1} and completely at delay 1 in Sect.~\ref{sect:delay1}. 
Concretely speaking, we will prove that at arity 1 and delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
Upper bounds for longer delays remain open. 
At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
At the delay 1 and arity 2, one infinite structure turns out to be foldable deterministically, which is the zigzag conformation shown in Fig.~\ref{TTT_zigzag}. 
These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}). 
Thus, the above mentioned upper bounds show that at delay 1 and arity 1, 3, or 4, or at delay 2 or 3 and arity 1, the class of deterministic unary oritatami systems is not Turing universal. 
The Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018} employs more than 500 types of beads. 
Thus, this weakness result is not surprising at all. 
The unary oritatami system might not be practical very much, though one bead may abstarct an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}). 
Nevertheless, this paper makes a first considerable step towards the characterization of non-Turing-universal oritatami systems.

@@

\begin{corollary}\label{cor:DTIME3}
	For fixed $\delta$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(|w|^3)$.
\end{corollary}
\begin{proof}
	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
\end{proof}

@@

\section{Case of arity $1$}\label{sect:arity1}

@@

\section{Case of delay $1$}\label{sect:delay1}
\input{tt_intro}
\input{tt_theorem}

\subsection*{Acknowledgements}
We thank Yo-Sub Han for his valuable comments on the contents of this paper.
